Contention Management for 5G

### 2017-05-05 article/article.tex
aa

      The following performance evaluation results compares the three presented algorithms.
      Notice that both the Greedy algorithm and the Shortest-Longest are polynomial time algorithm but are not always able to
      find optimal solutions. On the other hand, the exhaustive search will find it but it works in exponential time.
      We will compare the performance of the algorithms in two different regimes: the routes are either smaller than 
      the size of a message or they are arbitrary long.

>>>>

      The following performance evaluation results compares the three presented algorithms.
      Notice that both Greedy algorithm and the Shortest-Longest are polynomial time algorithm but are not always able to
      find optimal solutions. On the other hand, the exhaustive search will find an optimal solution, if it exists, but works in exponential time.
      We will compare the performance of the algorithms in two different regimes: the routes are either smaller than 
      the size of a message or they are arbitrary long.
